Using Machine Learning and Constraint Programming to Solve the Relational-To-Ontology Mapping Problem

### 2017-08-16 stp/paper_aaai/main.tex
Added stuff about unknown nodes

@@

\begin{flalign}
	& \text{Minimize~~} w_{STP} + w_{ADIFF} - w_{PAT}
	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
	%w_\mathcal{I}(e) + \sum_{e \in \mathcal{M}_\mathcal{O}^{s^\star}} c_e * 
    %		w_\mathcal{I}(e)
	\label{EQ:obj}&&\\
	&\text{such that~~}  \nonumber&& \\
	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
	&&\\
	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\
	&\forall d \in \mathcal{D_{G_O}}, c_d \Leftrightarrow degree(d) = 1 
	\label{EQ:deg2}&&\\
	&\forall a \in \mathcal{A}_{s^\star}, match[a] \in \{ d | (a,d)\in 
	\mathcal{M}_\mathcal{O}^{s^\star} \} \label{EQ:matchdom}&&\\
	& \textit{alldifferent}(match) \label{EQ:alld}&& \\
	& \forall a \in \mathcal{A}_{s^\star}, c_{match[a]} = \mathit{true} 
	\label{EQ:map}&&\\
	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
	\label{EQ:matchcost}  &&\\
	& \forall p \in \mathcal{P}, \big(\forall e\in edges(p), c_e = 
	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
	\label{EQ:pcost} 
\end{flalign}

Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
enforces that the solution 
$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
of the alignment graph 
and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. Eq. \ref{EQ:matchdom} ensures that the domain of each variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. Eq. 
\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph. Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute, which has to be one of 
the ones for which an edge existed. Eq. \ref{EQ:map} ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. Eq. 
\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by 
using patterns.

\section{Results \label{SEC:Res}}

>>>>

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham2016} or HTML 
tables \cite{ritze2017matching}.

For this reason, we add two artificial Class nodes to the integration graph:  
\emph{unknown} and \emph{root}. 
The latter will be connected to every other Class node in 
$\mathcal{V}_\mathcal{O}^{s^\star}$, including \emph{unknown}.
We also add a set $U = \{unk_1,...,unk_{|\mathcal{A}_{s^\star}|}\}$ of 
$|\mathcal{A}_{s^\star}|$ data 
nodes to the integration graph each connected to exactly one node in 
$\mathcal{A}_{s^\star}$ and to the \emph{unknown} Class node.

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. The rest of the attributes can then be matched normally 
and build  a semantic model as usual. Then, to maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the selected Class nodes will 
both be connected to the \emph{root} node. Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} won't be selected in the 
Steiner tree and the normal behavior will take place.
\ddg{Explain the weights of the edges introduced by the unknown nodes}

@@

\begin{flalign}
	& \text{Minimize~~} w_{STP} + w_{ADIFF} - w_{PAT}
	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
	%w_\mathcal{I}(e) + \sum_{e \in \mathcal{M}_\mathcal{O}^{s^\star}} c_e * 
    %		w_\mathcal{I}(e)
	\label{EQ:obj}&&\\
	&\text{such that~~}  \nonumber&& \\
	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
	&&\\
	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\
	&\forall d \in \mathcal{D_{G_O}}, c_d \Leftrightarrow degree(d) = 1 
	\label{EQ:deg2}&&\\
	&\forall a \in \mathcal{A}_{s^\star}, match[a] \in \{ d | (a,d)\in 
	\mathcal{M}_\mathcal{O}^{s^\star} \} \label{EQ:matchdom}&&\\
	& \textit{alldifferent}(match) \label{EQ:alld}&& \\
	& \forall a \in \mathcal{A}_{s^\star}, c_{match[a]} = \mathit{true} 
	\label{EQ:map}&&\\
	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
	\label{EQ:matchcost}  &&\\
	& \forall p \in \mathcal{P}, \big(\forall e\in edges(p), c_e = 
	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
	\label{EQ:pcost} &&\\
	& c_{unknown} \Rightarrow \big( c_{root}  \land 
	c_{(unknown,root)} \big) \label{EQ:unk}
\end{flalign}

Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
enforces that the solution 
$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
of the alignment graph 
and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. Eq. \ref{EQ:matchdom} ensures that the domain of each variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. Eq. 
\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph. Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute, which has to be one of 
the ones for which an edge existed. Eq. \ref{EQ:map} ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. Eq. 
\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by 
using patterns.
Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
is connected to \emph{root}.
Notice how there is no further requirement for unmatched attributes, as the 
$unk_i$ data nodes behave like normal data nodes, and the connectedness 
requirement will make sure that \emph{root} is connected to the rest of the 
tree (i.e. the semantic model).

Note how this CP model is easily adaptable to more classic settings where no 
patterns are used (by dropping Eqs. \ref{EQ:patt} and \ref{EQ:pcost}), or where 
the \emph{unknown} nodes are used (by dropping \ref{EQ:unk}).
\section{Results \label{SEC:Res}}
